\documentclass[sigconf]{acmart}

\input{format/final}

\begin{document}
\title{IoT and Big Data Analytics for Equipment Predictive Health
       Management (PHM)}

\author{Ashok Reddy Singam}
\orcid{HID337}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{711 N Park Ave}
  \city{Bloomington} 
  \state{Indiana} 
  \postcode{47408}
}
\email{asingam@iu.edu}

\author{Anil Ravi}
\orcid{HID333}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{711 N Park Ave}
  \city{Bloomington} 
  \state{Indiana} 
  \postcode{47408}
}
\email{anilravi@iu.edu}

\begin{abstract}
Not monitoring and gaining insight in to the industrial equipment in-service operational behavior has been the biggest bottleneck so far, which can be mitigated by using the latest IoT technologies. The idea is to collect the critical operational parameter data such as vibration, temperature, and load current from industrial equipment (compressors, vacuum generators, pumps, valves and any other rotating equipment applications etc.) and perform failure prediction analysis using KNN machine learning classification algorithms. The data will be collected from the field using wireless sensors (MQTT or CoAP protocols) and routed to cloud based AWS server via gateway/edge computing device. The collected data will be analyzed and made available to all stake holders to take appropriate preventive actions via web/mobile applications.

\end{abstract}

\keywords{i523, HID333, HID337}

\maketitle

\section{Introduction}

\section{TODO}

\section{Conclusion}

\begin{acks}

  The authors would like to thank professor Gregor von Laszewski and his team for providing \textit{LaTex} templates and assistance with the \textit{JabRef} tool to organize references.


\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 
\newpage
\appendix
\section{Work Breakdown}
\subsection{HID 333:Anil Ravi}
\begin{itemize}
  \item Identified Project topic.
  \item Created draft sections.
  \item Reviewed all sections of the paper.
\end{itemize}
\subsection{HID 337:Ashok Reddy Singam}
\begin{itemize}
  \item Editing Latex template using ShareLatex online tool.
  \item Managed JabRef entries.
  \item Reviewed the draft paper.
\end{itemize}



\end{document}
